Measuring Individual Partisan Harm in Redistricting

### 2021-10-12 paper/paper.Rmd

Harm is defined using the local, not global, utility measure, because inherently, global utility (and thus harm) will be constant for all voters of a particular party.
In fact, a harm measure defined analogously using global utility would essentially be a difference in seats won by a voter's party between plans $q$ and $\tilde q$ (the exact form would be affected by the function $g$).
A global harm measure is not particularly interesting, nor is it novel, being a standard measure of partisan harm in simulation-based redistricting litigation, up to a monotonic transformation [@2018league; @2019rucho; @2019lewis].
**[CM: revisit ¶ based on NJ findings].**

```{=html}
<!--  
With Harm defined, we can thus define Partisan Equity as: $E[H|V(I) = DEM] = E[H|V(I) = REP]$

Thus Fairness can be described as the signed movement away from equity. This naming works because it's condition on the votes and geographic distribution that you have, rather than some neutral midpoint that would be hard to justify.

This clarifies our QOI and by later focusing on fairness, that gives us the analogous connection between bias (symmetry) and fairness (equity).

Later, that also gives room in the discussion of the EGAP to talk about why you could describe a utility function based on $Pr(Vote not wasted)$, which 
-->
```
As with the utility measures, this harm measure naturally extends to multiple elections and districting plans.
Make the counterfactual plan a random variable $\tilde Q$, with $(V,Q,\tilde Q)\sim\pi$ such that $Q\indep\tilde Q$.
Then the harm to a random voter is $H \dfeq h(I, V, Q, \tilde Q)$.

>>>>

Harm is defined using the local, not global, utility measure, because inherently, global utility (and thus harm) will be constant for all voters of a particular party.
As we discuss below in Section \ref{subsec:diff-harm}, locally-based harm is connected to global electoral outcomes, anyway.

As with the utility measures, this harm measure naturally extends to multiple elections and districting plans.
Make the counterfactual plan a random variable $\tilde Q$, with $(V,Q,\tilde Q)\sim\pi$ such that $Q\indep\tilde Q$.
Then the harm to a random voter is $H \dfeq h(I, V, Q, \tilde Q)$.
